Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-06-20 prop_letter.tex
prop_letter.tex Fix a typo suggested by Prof. Hanson.

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
  [xr,x\ell] & \textrm{for }x\le0\textrm{ ,}
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of intervals to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators\nb\cite{Griffiths2003}, the last
condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
a direct counterpart of Eq.~\ref{eq:classicalconvex}.

>>>>

\begin{definition}[QIVPM]
  Given a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ and with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\textrm{ ;}\\{}
  [xr,x\ell] & \textrm{for }x\le0\textrm{ ,}
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  a QIVPM $\bar{\mu}$ is an assignment of an interval to each event
  (projection operator) subject to the following constraints:
  $\bar{\mu}(\mathbb{0})=\left[0,0\right]$,
  $\bar{\mu}(\mathbb{1})=\left[1,1\right]$,
  $\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$,
  and for each pair of \emph{commuting} projections $P_0$ and $P_1$,
  we have:
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
The first three constraints are the direct counterpart of the
corresponding ones for conventional probability measures. With the
understanding that the union of classical sets $E_1\cup E_2$ is replaced
by $P_0+P_1-P_0P_1$ in the case of projection operators\nb\cite{Griffiths2003}, the last
condition, Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, is
a direct counterpart of Eq.~\ref{eq:classicalconvex}.
